State of the Practice of Lattice Boltzmann Method Software Development

### 2021-07-28 StateOfPractice/Peter-Notes/Report/Report.tex
updated LBM report, organized 6.4

@@

@@

@@

@@

Documentation of LBM software is noted as being important, but its quality could be improved. As already noted, there is often no time or funding for maintaining quality documentation for software that is rarely used outside of the development team. Furthermore, the documentation generally only provides a shallow overview of the underlying CFD theory. Users would be well advised to already be familiar with these topics, or they should spend significant time referencing theory resources. The documentation instead generally focuses on explaining how to use the software. It is of course not feasible for package documentation to address the underlying physics topics in detail, so it is advised that the package documentation links to resources that better explain the underlying theory. Sometimes, frequently asked questions about the underlying theory are answered in the documentation. OpenLB has an artifact for such questions.

@@

@@

@@

The developer comments have emphasized an importance on source code, while documentation seems to be of secondary importance. It must be stressed that improving documentation could benefit development and help eliminate some of the developer concerns that were raised. The use of automatic document generation tools that capture scientific and computing knowledge, and transform it into software artifacts, is advised. Drasil is an automatic document generation tool that is further discussed in Section \ref{highlightedrecommendations}.

>>>>

\subsubsection{Lack of Development Time}

@@

\subsubsection{Lack of Software Development Experience}

@@

\subsubsection{Lack of Incentive and Funding}

@@

\subsubsection{Lack of External Support}

@@

\subsubsection{Parallelization and Continuous Integration}

@@

\subsubsection{Ensuring Correctness}

@@

\subsubsection{Technical Debt}

@@

\subsubsection{Quality of Documentation}

Interviewees commented that documentation is important and that its quality could be improved. As already noted, there is often no time or funding for maintaining quality documentation for software that is rarely used outside of the development team. Furthermore, the documentation generally only provides a shallow overview of the underlying CFD theory. Users would be well advised to already be familiar with these topics, or they should spend significant time referencing theory resources. The documentation instead generally focuses on explaining how to use the software. It is of course not feasible for package documentation to address the underlying physics topics in detail, so it is advised that the package documentation links to resources that better explain the underlying theory. Sometimes, frequently asked questions about the underlying theory are answered in the documentation. OpenLB has an artifact for such questions.

The developer comments emphasized an importance on source code, while documentation seems to be of secondary importance. It must be stressed that improving documentation could benefit development and help eliminate some of the developer concerns that were raised. The use of automatic document generation tools that capture scientific and computing knowledge, and transform it into software artifacts, is advised. Drasil is an automatic document generation tool that is further discussed in Section \ref{highlightedrecommendations}.
